Programming Language Survey Paper on Haskell

### 2013-04-22 projects/term_paper/paper.tex
Fixed a few typos.

\subsubsection{Type Checking}
Type checking in Haskell is performed statically at compile time. Haskell uses type-declarations for functions, in which the types of parameters and return values are explicitly defined. Any use of a function in which parameters do not meet the defined function type is flagged by the compiler, and compilation will be aborted. In addition, ues type inferencing by context. The type system in Haskell deduces obvious types and makes them concrete. In the following example, although the type of myNum is unknown at compile time, the compiler infers that the Int type is desired because myNum is added to an Int.

@@

The data type for each parameter of a function can be explicitly declared by using the ``::" symbol, which is read as ``has a type of." The types of the parameters can be listed in order, and the last type in the list is the return type. The following function is called ``greet."
It takes in a string and returns a string. The string is passed in as the variable ``name." Everything that follows the equal sign is the expression, and the evaluation of this expression is the return value.

@@

In the following example, an input of ``Haskell" will produce the first expression, ``Clojure" will skip the first and produce the second, and any other input will produce the third. Note that the third and final expression does not have a pattern to match, but instead uses a variable to catch all other input.

>>>>

\subsubsection{Type Checking}
Type checking in Haskell is performed statically at compile time. Haskell uses type-declarations for functions, in 
which the types of parameters and return values are explicitly defined. Any use of a function in which parameters 
do not meet the defined function type is flagged by the compiler, and compilation will be aborted. In addition, 
use type inferencing by context. The type system in Haskell deduces obvious types and makes them concrete. In the 
following example, although the type of myNum is unknown at compile time, the compiler infers that the Int type 
is desired because myNum is added to an Int.

@@

The data type for each parameter of a function can be explicitly declared by using the ``::" symbol, which is 
read as ``has a type of." The types of the parameters can be listed in order, and the last type in the list 
is the return type. The following function is called ``greet."

It takes in a string and returns a string. The string is passed in as the variable ``name." Everything that follows the equal sign is the expression, and the evaluation of this expression is the return value.

@@

In the following example, an input of ``Haskell'' will produce the first expression, ``Clojure'' will skip the first 
and produce the second, and any other input will produce the third. Note that the third and final expression does 
not have a pattern to match, but instead uses a variable to catch all other input.
